Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-03 manuscript.Rmd
More edits to intro

We contextualize linguistic cohesion with social mobilization and response to
the relative intensity of the conflict. Cohesion is a multi-layered concept
referring to the connectedness of speakers, actions, and societies. Cohesion
reflects the continuity of language and expression, and it shows the
connectivity of participants in a social movement. To address the relationship
between language and discourse and social movements, we adopt an
interdisciplinary approach that incorporates linguistics, psychology, and
political science using nonlinear dynamical systems methodology to model the
relationship between language and action.

@@

Just as real-world social cohesion can be quantified, so can online cohesion.
One kind of cohesion can be found in the similarity in language use on social
media. This implicit or explicit similarity in language use can indicate shared
beliefs, thoughts, and feelings, as has been studied in research on language
style in psycholinguistics and social psychology [@gonzales2010language;
@tausczik2010psychological;
@brennan1996conceptual]. Although previous work on language style has often
focused on individuals and small groups, this can be scaled up to examine
massive social-level changes [@michel2011quantitative; @fusaroli2015timescales].

@@

Thus, lexical and interpersonal cohesion are hypothesized to be tied to social
and political cohesion. Shared language in an online environment may lead to the
development or expression of a shared identity [@wiltermuth2009synchrony]. This,
in turn, may drive individuals' propensity to engage in similar coordinated
behavior on behalf of the group [@wiltermuth2009synchrony; @walton2012mere].
Taken together, these two processes may grow movement participants' weak and
strong ties [@granovetter1977strength; @gladwell2010revolution;
@mcadam1986recruitment], strengthening the movement overall by expanding and
deepening heterogenous ties. Therefore, in the context of social conflict, the
linguistic cohesion of the online conversation should correspond to the degree
of social cohesion on the ground.

Steinert-Threlkeld [-@steinert2017spontaneous] modeled a similar relationship
between social media and social mobilization alongside event data. That
groundbreaking work demonstrated that participants on the fringe of a social
movement contribute substantially to the overall level of protest. In addition
to providing new methods to this growing field of study, we build on this
previous work by demonstrating how sociolinguistic cohesion evolves in
response to negative and positive exogenous events.

>>>>

We contextualize linguistic cohesion with social mobilization and response to
the relative intensity of the conflict. Cohesion is a multi-layered concept
referring to the connectedness of speakers, actions, and societies. It
reflects the continuity of language and expression, and shows the
connectivity of participants in a social movement. To address the relationship
between language and discourse and social movements, we adopt an
interdisciplinary approach that incorporates linguistics, psychology, and
political science using nonlinear dynamical systems methodology to disentangle the
relationship between language and action.

@@

Just as real-world social cohesion can be quantified, so can online cohesion.
One kind of cohesion is the similarity in language use on social
media. This implicit or explicit similarity can indicate shared
beliefs, thoughts, and feelings, as has been studied in research on language
style in psycholinguistics and social psychology [@gonzales2010language;
@tausczik2010psychological;
@brennan1996conceptual]. Although previous work on language style has often
focused on individuals and small groups, this can be scaled up to examine
massive social-level changes [@michel2011quantitative; @fusaroli2015timescales].

@@

Thus, lexical and interpersonal cohesion are hypothesized to be tied to social
and political cohesion. Shared language in an online environment may lead to the
development or expression of a shared identity [@wiltermuth2009synchrony]. This,
in turn, may drive individuals' propensity to engage in similar coordinated
behavior on behalf of the group [@wiltermuth2009synchrony; @walton2012mere].
Taken together, these two processes may increase movement participants' weak and
strong ties [@granovetter1977strength; @gladwell2010revolution;
@mcadam1986recruitment], strengthening the movement overall by expanding and
deepening heterogenous ties. Therefore, in the context of social conflict, the
linguistic cohesion of the online conversation should correspond to the degree
of social cohesion on the ground.

Steinert-Threlkeld [-@steinert2017spontaneous] modeled a similar relationship
between social media and social mobilization alongside event data. That
groundbreaking work demonstrated that participants on the fringe of a social
movement contribute substantially to the overall level of protest. In addition
to providing new methods to this growing field of study, we build on this
previous work by demonstrating how sociolinguistic cohesion evolves in
tandem with negative and positive exogenous events.
